---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# powertools

<!-- badges: start -->
<!-- badges: end -->

The goal of powertools is to provide Power and Sample Size Tools in R for researchers. This package accompanies the text "Power and Sample Size in R" by Catherine M. Crespi. 

This package loads all R packages that are used in the textbook and provides new functions for sample size and power calculations that did not previously exist.

## Installation

You can install the development version of `powertools` like so:

``` r
# install.packages("devtools")
devtools::install_github("zichen-liu/powertools")
```

## Example

A study hopes to show whether or not a new experimental therapy is promising. A treatment is considered promising if at least 20% of participants respond well, and the researchers believe that the true response proportion is 30%. This is a basic example that show how to calculate the sample size needed for this study to achieve 80% power, following Example 6.1 in the textbook.

```{r example}
library(powertools)
prop.1samp(N = NULL, p0 = 0.2, pA = 0.3, power = 0.8, sides = 1)
```

`prop.1samp` returns n, the required sample size for a one proportion test. 
